\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-23 paper.qmd
Changed formula to obtain binwidth
working on binning the data section

$$
b_1 = \frac{r_1 + q_1}{a_1}.
$$

@@

$$
b_2 = \frac{r_2 + q_2}{0.75 \times a_2}.
$$

@@

#### Hexagon binning

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($a_2$), width ($a_1$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $a_1$, and $a_2$.

>>>>

$$
a_1 = \frac{r_1 + q_1}{b_1}.
$$

@@

$$
a_2 = \frac{r_2 + q_2}{0.75 \times b_2}.
$$

@@

#### Binning the data

Points are allocated to the bin that they fall in. XXX How are you doing this? Do you check the bounds of the hexagon? Or do you use distance to centroid?

<!--
Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($a_2$), width ($a_1$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $a_1$, and $a_2$. 
-->

### 2024-04-23 paper.tex
Changed formula to obtain binwidth
working on binning the data section

\[
b_1 = \frac{r_1 + q_1}{a_1}.
\]

@@

\[
b_2 = \frac{r_2 + q_2}{0.75 \times a_2}.
\]

\subsubsection{Hexagon binning}\label{hexagon-binning}

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(a_2\)), width (\(a_1\)). Each of the \kD{} points will
belong to a hexagonal bin. That is, for each \(y \in \mathbfit{Y}\), we
can (uniquely) identify the hexagon that the point belongs to. This
identification is done finding the nearest bin centroid for the \kD{}
points by considering the \kD{} Euclidean distance.

When \(k=2\), the starting coordinates \((s_1, s_2)\) mark the lower
left of the grid. This is the bottom left bin centroid. By starting from
there, points are generated to fill the grid accounting \(b_1\),
\(b_2\), \(a_1\), and \(a_2\).

>>>>

\[
a_1 = \frac{r_1 + q_1}{b_1}.
\]

@@

\[
a_2 = \frac{r_2 + q_2}{0.75 \times b_2}.
\]

\subsubsection{Binning the data}\label{binning-the-data}

Points are allocated to the bin that they fall in. XXX How are you doing
this? Do you check the bounds of the hexagon? Or do you use distance to
centroid?
